Who does big team science?

### 2023-03-23 manuscript_scopus.Rmd
updated pictures

small_dot <- ggplot(small_effect, aes(year,v)) + 
  geom_point(aes(size = people)) + 
  theme_classic() + 
  geom_pointrange(aes(ymin = low, ymax = high)) + 
  xlab("Year") + 
  ylab(expression(R^2)) + 
  scale_size_continuous(name = "Num Authors")

@@

medium_dot <- ggplot(medium_effect, aes(year,v)) + 
  geom_point(aes(size = people)) + 
  theme_classic() + 
  geom_pointrange(aes(ymin = low, ymax = high)) + 
  xlab("Year") + 
  ylab(expression(R^2)) + 
  scale_size_continuous(name = "Num Authors")

@@

large_dot <- ggplot(large_effect, aes(year,v)) + 
  geom_point(aes(size = people)) + 
  theme_classic() + 
  geom_pointrange(aes(ymin = low, ymax = high)) + 
  xlab("Year") + 
  ylab(expression(R^2)) + 
  scale_size_continuous(name = "Num Authors")

@@

```{r effect-gpe-figure, include = TRUE}
small_dot + 
  theme(legend.position = "none") + 
  coord_cartesian(ylim = c(0,1)) +
  ggtitle("10-49 Authors") + 
medium_dot + 
  theme(legend.position = "none") + 
  coord_cartesian(ylim = c(0,1)) +
  ggtitle("50-99 Authors") +
large_dot + 
  theme(legend.position = "none") + 
  coord_cartesian(ylim = c(0,1)) +
  ggtitle("100 + Authors") + 
guide_area() + 
plot_layout(
  ncol = 2,
  nrow = 2, 
  guides = "collect")

>>>>

small_dot <- ggplot(small_effect, aes(year,v)) + 
  geom_point(aes(size = people)) + 
  theme_classic() + 
  geom_pointrange(aes(ymin = low, ymax = high)) + 
  xlab("Year") + 
  ylab(expression(phi)) + 
  scale_size_continuous(name = "Num Authors")

@@

medium_dot <- ggplot(medium_effect, aes(year,v)) + 
  geom_point(aes(size = people)) + 
  theme_classic() + 
  geom_pointrange(aes(ymin = low, ymax = high)) + 
  xlab("Year") + 
  ylab(expression(phi)) + 
  scale_size_continuous(name = "Num Authors")

@@

large_dot <- ggplot(large_effect, aes(year,v)) + 
  geom_point(aes(size = people)) + 
  theme_classic() + 
  geom_pointrange(aes(ymin = low, ymax = high)) + 
  xlab("Year") + 
  ylab(expression(phi)) + 
  scale_size_continuous(name = "Num Authors")

@@

```{r effect-gpe-figure, include = TRUE}
small_dot + 
  theme(legend.position = "none") + 
  coord_cartesian(ylim = c(0,1), xlim = c(1980, 2025)) +
  ggtitle("10-49 Authors") + 
medium_dot + 
  theme(legend.position = "none") + 
  coord_cartesian(ylim = c(0,1), xlim = c(1980, 2025)) +
  ggtitle("50-99 Authors") +
large_dot + 
  theme(legend.position = "none") + 
  coord_cartesian(ylim = c(0,1), xlim = c(1980, 2025)) +
  ggtitle("100 + Authors") + 
guide_area() + 
plot_layout(
  ncol = 2,
  nrow = 2, 
  guides = "collect")
